Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-05-16 tex/ms.tex
tweaking

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened.  We got data which were uncalibrated and data
which had been approximately spectrophotometrically calibrated using
an average for the night (MORE HERE).  Show figure of calibrated and
uncalibrated data.  Discuss S/N, sky subtraction, calibration.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.

Our prior distributions are in all cases top-hat functions, though
more informative prior distributions may be used.  Informative priors
may be especially appropriate for the calibration parameters $\alpha$
if additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

@@

>>>>

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened.  We got data which were uncalibrated and data
which had been approximately spectrophotometrically calibrated using
an average for the night (MORE HERE). Figure \ref{fig:data} shows the
calibrated and uncalibratred spectra for each cluster.  Discuss S/N,
sky subtraction, calibration.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

We estimate the posterior through MCMC sampling after an initial round
of optimization using Powell's method.  The specific sampling
algorithm we use is the affine-invariant ensemble sampling scheme of
\citet{GW}, as implemented in the \texttt{emcee} package \cite{dfm}
Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
sampler does not require the specification of step sizes in each
dimension.  ASSESSING SAMPLER CONVERGENCE

Our prior distributions are in all cases top-hat functions, though
more informative prior distributions may be used.  Informative priors
may be especially appropriate for the calibration parameters $\alpha$
if additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case that there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

@@

Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.

Finally, we have fun playing with the number of photometric bands and the S/N.
